%!TEX program = pdflatex
\documentclass[11pt, letterpaper]{article}

% ---- Packages ----
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{tgpagella}              % Palatino-style serif
\usepackage[scaled=0.88]{berasans}  % Clean sans-serif for headings
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tabularx}
\usepackage{etaremune}  % reverse-numbered lists

% ---- Colors ----
\definecolor{accent}{HTML}{1a2332}
\definecolor{link}{HTML}{2563eb}
\definecolor{rule}{HTML}{cbd5e1}
\definecolor{light}{HTML}{64748b}

% ---- Hyperlinks ----
\hypersetup{
  colorlinks=true,
  linkcolor=link,
  urlcolor=link,
  pdfauthor={S. Parker Singleton},
  pdftitle={Curriculum Vitae},
}

% ---- Section Formatting ----
\titleformat{\section}
  {\Large\sffamily\bfseries\color{accent}}
  {}
  {0em}
  {}
  [\vspace{-0.6em}\textcolor{rule}{\rule{\linewidth}{0.8pt}}]

\titlespacing*{\section}{0pt}{1.2em}{0.6em}

\titleformat{\subsection}
  {\normalsize\sffamily\bfseries\color{accent}}
  {}
  {0em}
  {}

\titlespacing*{\subsection}{0pt}{0.8em}{0.3em}

% ---- List Formatting ----
\setlist[itemize]{leftmargin=1.5em, itemsep=2pt, parsep=0pt, topsep=3pt}
\setlist[enumerate]{leftmargin=1.5em, itemsep=2pt, parsep=0pt, topsep=3pt}

% ---- Header / Footer ----
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small\color{light} S.\ Parker Singleton \textbullet\ Curriculum Vitae \textbullet\ Page \thepage\ of \pageref{LastPage}}

% ---- Custom Commands ----
\newcommand{\entry}[4]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}p{3.1cm}X@{}}
    \textcolor{light}{\small #1} &
    \textbf{#2} \\
    & \textit{#3} \\
    & #4
  \end{tabularx}
  \vspace{0.4em}
}

\newcommand{\entryshort}[3]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}p{3.1cm}X@{}}
    \textcolor{light}{\small #1} &
    \textbf{#2} \\
    & \textit{#3}
  \end{tabularx}
  \vspace{0.3em}
}

\newcommand{\me}{\textbf{S.\ P.\ Singleton}}

% ============================================================
\begin{document}
\thispagestyle{fancy}

% ---- Title Block ----
\begin{center}
  {\Huge\sffamily\bfseries\color{accent} S.\ Parker Singleton}\\[0.5em]
  {\small
    \href{mailto:sps253@cornell.edu}{sps253@cornell.edu}
    \enspace\textbullet\enspace
    \href{https://singlesp.github.io}{singlesp.github.io}
    \enspace\textbullet\enspace
    \href{https://sypres.io}{sypres.io}
  }
\end{center}

\vspace{0.5em}

% ================================================================
\section{Education}
% ================================================================

\entryshort{2020 -- 2023}{Ph.D.\ Computational Biology}{Cornell University}

\entryshort{2015 -- 2017}{M.S.\ Chemistry}{Cornell University}

\entryshort{2011 -- 2015}{B.S.\ Chemistry}{University of South Carolina}

% ================================================================
\section{Professional Experience}
% ================================================================

\entry{2025 -- Present}
  {Senior Scientist}
  {Penn Lifespan Informatics and Neuroimaging Center (PennLINC), University of Pennsylvania}
  {Advisor: Theodore D.\ Satterthwaite \newline
   Research and development lead for \href{https://sypres.io}{SYPRES} --- an initiative to present high-quality living evidence synthesis in clinical psychedelics. \newline
   Member of the neuroinformatics team: neuroimaging dataset curation, analysis, and release; full-stack software engineering.}

\entry{2024 -- 2025}
  {Postdoctoral Researcher}
  {Penn Lifespan Informatics and Neuroimaging Center (PennLINC), University of Pennsylvania}
  {Advisor: Theodore D.\ Satterthwaite \newline
   Assessed the clinical efficacy and risks of psychedelic-assisted therapies. \newline
   Developed new tools and frameworks for measuring psychedelic-induced functional plasticity in the brain using fMRI.}

\entry{2023 -- 2024}
  {Postdoctoral Researcher}
  {Computational Connectomics Lab, Weill Cornell Medicine}
  {Advisor: Amy Kuceyeski \newline
   Studied the effects of pharmacology, substance use, and trauma on human brain activity/connectivity using network control theory and multimodal neuroimaging. \newline
   Mentored undergraduate and graduate students on rotation and thesis projects.}

\entry{2020 -- 2023}
  {NSF Graduate Research Fellow}
  {Department of Computational Biology, Cornell University}
  {Advisor: Amy Kuceyeski \newline
   Studied the effects of psychedelics on human brain activity/connectivity in the Computational Connectomics Lab. \newline
   Utilized advanced techniques in network control theory, statistics, and machine learning to quantify brain dynamics. \newline
   Identified neural correlates of MDMA-assisted therapy for PTSD using audio script-driven memory recollection during fMRI.}

\entry{2017 -- 2020}
  {High School Teacher}
  {Palmetto Scholars Academy, North Charleston, SC}
  {Designed and implemented a diverse 10th grade chemistry curriculum for intellectually gifted students. \newline
   Instructor of dual-enrollment Chemistry 110/111 lecture and lab. \newline
   Instructor of Introduction to Research course preparing juniors for their senior capstone project. \newline
   Utilized a project-based-learning curriculum for an experimental chemistry elective.}

\entry{2015 -- 2017}
  {Graduate Research Assistant}
  {Department of Chemistry \& Chemical Biology, Cornell University}
  {Advisor: Brett P.\ Fors \newline
   Developed novel catalyst systems for controlling polymer topology \textit{in situ}, utilizing visible light as an external stimulus. \newline
   Structure--property relationships studied via NMR, rheology, and SAXS. \newline
   Random forest classifier implemented to map structure--property relationships.}

\entry{2013 -- 2015}
  {Undergraduate Researcher}
  {Department of Chemistry \& Biochemistry, University of South Carolina}
  {Advisor: Chuanbing Tang \newline
   Development and classification of cationic, rosin acid-derived compounds and polymers as novel antimicrobial agents. \newline
   Surface-initiated ATRP modification of glass surfaces for medical device and implant applications.}

\entry{2013 -- 2014}
  {Applications/Development Chemist Intern I \& II}
  {MeadWestvaco (now Ingevity), North Charleston, SC}
  {Performed ladder studies involving HM-PSA formulation and preparation, physical and rheological testing, followed by multivariate analysis (PCA, PLSA) for iterative product screening. \newline
   Explored synthetic pathways for the development of new products with targeted end-use properties in adhesive systems.}

% ================================================================
\section{Publications}
% ================================================================

\subsection{Original Research}

\begin{etaremune}[itemsep=5pt]
  \item P.\ Mallaroni, \me, N.\ L.\ Mason, T.\ D.\ Satterthwaite, J.\ G.\ Ramaekers.
    ``Spatiotemporal mapping of brain organisation following the administration of 2C-B and psilocybin.''
    \textit{Molecular Psychiatry}, 2026.
    \href{https://doi.org/10.1038/s41380-026-03447-0}{doi: 10.1038/s41380-026-03447-0}.

  \item A.\ I.\ Luppi, L.\ Uhrig, J.\ Tasserie, P.\ A.\ M.\ Mediano, F.\ E.\ Rosas, \me, D.\ Gutierrez-Barragan, S.\ Gini, P.\ Castro, C.\ M.\ Signorelli, D.\ Golkowski, A.\ Ranft, R.\ Ilg, D.\ Jordan, K.\ Muta, J.\ Hata, H.\ Okano, Z.-Q.\ Liu, Y.\ Yee, A.\ Destexhe, R.\ Cofre, D.\ K.\ Menon, A.\ Gozzi, B.\ Jarraya, E.\ A.\ Stamatakis.
    ``Convergent transcriptomic and connectomic controllers of information integration and its anaesthetic breakdown across mammalian brains.''
    \textit{Nature Human Behaviour}, 2025.
    \href{https://doi.org/10.1038/s41562-025-02381-5}{doi: 10.1038/s41562-025-02381-5}.

  \item L.\ Schilling, \me, C.\ Tozlu, M.\ H\'{e}do, Q.\ Zhao, K.\ M.\ Pohl, K.\ Jamison, A.\ Kuceyeski.
    ``Sex-specific differences in brain activity dynamics of youth with a family history of substance use disorder.''
    \textit{Nature Mental Health}, 2025.
    \href{https://doi.org/10.1038/s44220-025-00523-2}{doi: 10.1038/s44220-025-00523-2}.

  \item D.\ P.\ Kelley, \me, K.\ Venable, G.\ Sturm, A.\ Skovgaard, J.\ Francis, T.\ C.\ Neylan, E.\ R.\ Bradley, J.\ Woolley, M.\ Picard, A.\ O'Donovan.
    ``The allostatic triage model of psychopathology (ATP Model): How reallocation of brain energetic resources under stress elicits psychiatric symptoms.''
    \textit{Neuroscience \& Biobehavioral Reviews}, 2025.
    \href{https://doi.org/10.1016/j.neubiorev.2025.106419}{doi: 10.1016/j.neubiorev.2025.106419}.

  \item N.\ Roy, \me, K.\ Jamison, P.\ Mukherjee, S.\ A.\ Shah, A.\ Kuceyeski.
    ``Brain activity dynamics after traumatic brain injury indicate increased state transition energy and preference of lower order states.''
    \textit{NeuroImage: Clinical}, 2025.
    \href{https://doi.org/10.1016/j.nicl.2025.103799}{doi: 10.1016/j.nicl.2025.103799}.

  \item \me, C.\ Timmermann, A.\ I.\ Luppi, E.\ Eckern\"{a}s, L.\ Roseman, R.\ L.\ Carhart-Harris, A.\ Kuceyeski.
    ``Network control energy reductions under DMT relate to serotonin receptors, signal diversity, and subjective experience.''
    \textit{Communications Biology}, 2025.
    \href{https://doi.org/10.1038/s42003-025-08078-9}{doi: 10.1038/s42003-025-08078-9}.

  \item A.\ I.\ Luppi, \me, J.\ Y.\ Hansen, K.\ W.\ Jamison, D.\ Bzdok, A.\ Kuceyeski, R.\ F.\ Betzel, B.\ Misic.
    ``Contributions of network structure, chemoarchitecture and diagnostic categories to transitions between cognitive topographies.''
    \textit{Nature Biomedical Engineering}, 2024.
    \href{https://doi.org/10.1038/s41551-024-01242-2}{doi: 10.1038/s41551-024-01242-2}.

  \item \me, P.\ Velidi, L.\ Schilling, A.\ I.\ Luppi, K.\ Jamison, L.\ Parkes, A.\ Kuceyeski.
    ``Altered structural connectivity and functional brain dynamics in individuals with heavy alcohol use elucidated via network control theory.''
    \textit{Biological Psychiatry: Cognitive Neuroscience and Neuroimaging}, 2024.
    \href{https://doi.org/10.1016/j.bpsc.2024.05.006}{doi: 10.1016/j.bpsc.2024.05.006}.

  \item \me.
    ``This Is Your Brain on Drugs: A Multimodal Neuroimaging and Computational Investigation into the Effects of Psychedelic Tryptamines and MDMA on Human Brain Dynamics.''
    \textit{Doctoral Dissertation, Cornell University; ProQuest Dissertations \& Theses}, 2023. 30420106.

  \item \me, J.\ B.\ Wang, M.\ Mithoefer, C.\ Hanlon, M.\ S.\ George, A.\ Mithoefer, O.\ Mithoefer, A.\ R.\ Coker, B.\ Yazar-Klosinski, A.\ Emerson, R.\ Doblin, A.\ Kuceyeski.
    ``Altered brain activity and functional connectivity after MDMA-assisted therapy for post-traumatic stress disorder.''
    \textit{Frontiers in Psychiatry}, 2023; 13:947622.
    \href{https://doi.org/10.3389/fpsyt.2022.947622}{doi: 10.3389/fpsyt.2022.947622}.

  \item \me, A.\ I.\ Luppi, R.\ L.\ Carhart-Harris, J.\ Cruzat, L.\ Roseman, D.\ J.\ Nutt, G.\ Deco, M.\ L.\ Kringelbach, E.\ A.\ Stamatakis, A.\ Kuceyeski.
    ``Receptor-informed network control theory links LSD and psilocybin to a flattening of the brain's control energy landscape.''
    \textit{Nature Communications}, 2022.
    \href{https://doi.org/10.1038/s41467-022-33578-1}{doi: 10.1038/s41467-022-33578-1}.

  \item M.\ Nadgorny, D.\ T.\ Gentekos, Z.\ Xiao, \me, B.\ P.\ Fors, L.\ A.\ Connal.
    ``Manipulation of Molecular Weight Distribution Shape as a New Strategy to Control Processing Parameters.''
    \textit{Macromolecular Rapid Communications}, 2017.
    \href{https://doi.org/10.1002/marc.201700352}{doi: 10.1002/marc.201700352}.

  \item M.\ S.\ Ganewatta, K.\ P.\ Miller, \me, P.\ Mehrpouya-Bahrami, Y.\ P.\ Chen, Y.\ Yan, M.\ Nagarkatti, P.\ Nagarkatti, A.\ W.\ Decho, C.\ Tang.
    ``Antibacterial and Biofilm-Disrupting Coatings from Resin Acid-Derived Materials.''
    \textit{Biomacromolecules}, 2015.
    \href{https://doi.org/10.1021/acs.biomac.5b01005}{doi: 10.1021/acs.biomac.5b01005}.
\end{etaremune}

\subsection{Commentaries \& Perspectives}

\begin{itemize}[label=\textbullet]
  \item \me, B.\ L.\ Sevchik, S.\ N.\ Vandekar, E.\ C.\ Strain, S.\ M.\ Nayak, R.\ H.\ Dworkin, J.\ C.\ Scott, T.\ D.\ Satterthwaite.
    ``An initiative for living evidence synthesis in clinical psychedelic research.''
    \textit{Nature Mental Health}, 2025.
    \href{https://doi.org/10.1038/s44220-024-00373-4}{doi: 10.1038/s44220-024-00373-4}.

  \item \me, A.\ Kuceyeski.
    ``Bridging Psilocybin-Induced Changes in the Brain's Dynamic Functional Connectome With an Individual's Subjective Experience.''
    \textit{Biological Psychiatry: Cognitive Neuroscience and Neuroimaging}, 2024.
    \href{https://doi.org/10.1016/j.bpsc.2024.05.003}{doi: 10.1016/j.bpsc.2024.05.003}.
\end{itemize}

% ================================================================
\section{Presentations}
% ================================================================

\subsection{Invited Talks, Panels \& Workshops}

\begin{itemize}
  \item ``Novel treatments for PTSD: focus on fear conditioning as a translational model.'' The Winter Conference on Brain Research, Lake Tahoe, 2025.
  \item ``Pharmacologically-informed network control theory.'' The Nora Volkow group at the National Institute on Alcohol Abuse and Alcoholism, online, 2023.
  \item ``Unlocking DMT Horizons: Exploring the clinical potential of DMT.'' OPEN Foundation, online, 2023.
  \item ``Harnessing neural and cognitive plasticity with psychedelics.'' Cleveland Clinic Psychedelic Science Group, online, 2022.
  \item ``Modeling brain dynamics using psychedelics.'' Maastricht University, Netherlands, 2022.
  \item ``The flowing brain on psychedelics.'' Oxford Psychedelic Society, online, 2021.
  \item ``Chemistry and Music Workshop.'' American Chemical Society National Meeting, Orlando, FL, 2019.
\end{itemize}

\subsection{Oral Presentations}

\begin{itemize}
  \item ``This is your brain on drugs: A multimodal neuroimaging and computational investigation into the effects of psychedelics and MDMA on human brain dynamics.'' Dissertation Defense Seminar, Department of Computational Biology, Cornell University, 2023.
  \item ``Altered neural activity patterns following MDMA-assisted therapy for PTSD: an fMRI pilot study.'' Interdisciplinary Conference on Psychedelic Research, Haarlem, Netherlands, 2022.
  \item ``A flattened energy landscape under LSD and psilocybin: how psychedelics advance our ability to model brain dynamics.'' Psychedemia: Neuroscience Panel, Columbus, OH, 2022.
  \item ``Evidence for a flattened energy landscape under LSD and Psilocybin.'' Canadian Computational Neuroscience Spotlight, online, 2022.
  \item ``Neurobiology of MDMA-assisted therapy for PTSD.'' Cornell Computational Biology Student Seminar Series, Ithaca, NY, 2022.
  \item ``LSD flattens the brain's energy landscape: insights from receptor-informed network control theory.'' Cornell Computational Biology Student Seminar Series, Ithaca, NY, 2021.
  \item ``Antibacterial and Biofilm-Disrupting Coating Sustainable Materials.'' University of South Carolina Discovery Day for Undergraduate Researchers, Columbia, SC, 2015.
  \item ``Antibacterial and Biofilm-Disrupting Coating Sustainable Materials.'' Southeastern Undergraduate Research Conference, Montgomery, AL, 2015.
\end{itemize}

\subsection{Poster Presentations}

\begin{itemize}
  \item ``A living systematic review, meta-analysis, and open data resource of trials of psilocybin treatment for symptoms of depression.'' ACNP, Hollywood, FL, 2025.
  \item ``A living systematic review, meta-analysis, and open data resource of trials of psilocybin treatment for symptoms of depression.'' Gordon Research Conference: Neurobiology of Psychedelics, Smithfield, RI, 2025.
  \item ``Altered structural connectivity and functional brain dynamics in individuals with heavy alcohol use elucidated via network control theory.'' Organization for Human Brain Mapping, Seoul, South Korea, 2024.
  \item ``Time-resolved network control analysis of human brain dynamics under DMT.'' Organization for Human Brain Mapping, Montreal, Canada, 2023.
  \item ``Altered brain activity and functional connectivity after MDMA-assisted therapy for post-traumatic stress disorder.'' Psychedelic Science 2023, Denver, CO, 2023.
  \item ``LSD and psilocybin flatten the brain's energy landscape: insights from receptor-informed network control theory.'' Organization for Human Brain Mapping, Glasgow, U.K., 2022.
  \item ``Evidence for altered neural activity patterns after MDMA-assisted therapy in adults with chronic and severe PTSD: a pilot study.'' Organization for Human Brain Mapping, Glasgow, U.K., 2022.
  \item ``LSD and psilocybin flatten the brain's energy landscape: insights from receptor-informed network control theory.'' From Research to Reality: Global Summit on Psychedelic Therapies and Medicine, Toronto, CA, 2022.
  \item ``Evidence for altered neural activity patterns after MDMA-assisted therapy in adults with chronic and severe PTSD: a pilot study.'' From Research to Reality: Global Summit on Psychedelic Therapies and Medicine, Toronto, CA, 2022.
  \item ``LSD flattens the brain's energy landscape: insights from receptor-informed network control theory.'' Organization for Human Brain Mapping, online, 2021.
  \item ``Sustainable Antimicrobial Coatings from Resin Acids.'' American Chemical Society Awards Day, Orangeburg, SC, 2014.
\end{itemize}

% ================================================================
\section{Teaching \& Outreach}
% ================================================================

\entryshort{2023 -- Present}
  {Machine Learning in Medicine Virtual Seminar Series}
  {Cornell University}
\vspace{-0.3em}
\begin{itemize}
  \item Inter-campus collaborative bringing together researchers with common interests in machine learning applied to clinical questions and data.
  \item Invite and host speakers from academia and industry for regular virtual seminar series.
\end{itemize}
\vspace{0.3em}

\entryshort{2019 -- 2022}
  {Advisor, High School Senior Capstone Experience}
  {Palmetto Scholars Academy, North Charleston, SC}
\vspace{-0.3em}
\begin{itemize}
  \item Mentored high school students to develop, plan, and perform thesis research; students carry out hands-on research, write a thesis, and defend before a committee.
\end{itemize}
\vspace{0.3em}

\entryshort{2017 -- 2018}
  {Head Coach, VEX High School Robotics}
  {Palmetto Scholars Academy, North Charleston, SC}
\vspace{-0.3em}
\begin{itemize}
  \item Coached 4 teams during the 2017--2018 In The Zone challenge; teams earned 2 Excellence Awards, 2 Design Awards, and 1 Tournament Champions award; 2 teams advanced to SC State Tournament; 1 advanced to the US CREATE Open.
\end{itemize}
\vspace{0.3em}

\entryshort{2016 -- 2017}{Outreach Coordinator}{Fors Research Group, Cornell University}

\entryshort{2015 -- 2017}{Families Learning Science Together Workshop Volunteer}{Cornell Center for Materials Research}

\entryshort{2015 -- 2016}{Graduate Teaching Assistant, Organic Chemistry Lab}{Cornell University}

\entryshort{Oct -- Nov 2015}{Family Science Nights Module Instructor}{Sciencenter Museum, Ithaca, NY}

\entryshort{Jan -- May 2013}{Teaching Assistant, General Chemistry Lab}{University of South Carolina}

% ================================================================
\section{Honors \& Awards}
% ================================================================

\begin{tabularx}{\linewidth}{@{}lX@{}}
  2022 & Fulbright Research Grant Alternate \\
  2016 -- 2022 & National Science Foundation Graduate Research Fellowship \\
  2015 & Graduation with Leadership Distinction in Research \\
  2015 & University of South Carolina Outstanding Senior Award \\
  2015 & Who's Who Among American Colleges and Universities Award \\
  2015 & Hypercube Scholar Award \\
  2014 & Hiram S.\ and Lawanda Allen Scholarship for Excellence in Chemistry \\
  2014 & Magellan Scholarship for Undergraduate Research \\
  2014 & Outstanding Poster Presentation, SC ACS Awards Day \\
  2011 -- 2015 & South Carolina Palmetto Fellows Scholar \\
  2011 -- 2015 & USC Dean's Scholar \\
\end{tabularx}

% ================================================================
\section{Volunteer Experience}
% ================================================================

\entryshort{2017 -- 2023}{President, Homeowner's Association}{Jericho on the Ashley, North Charleston, SC}

\entryshort{October 2016}{Service Volunteer}{Montgomery Park Playground Build, Dryden, NY}

\entryshort{2013 -- 2015}{President \& Founder, Recycling Committee}{Gates at Williams-Brice, Columbia, SC}

\entryshort{Summers 2013--14}{Service Volunteer}{The Hope Lodge, American Cancer Society, Charleston, SC}

\end{document}

