%!TEX program = pdflatex
\documentclass[10pt, letterpaper]{article}

% ---- Packages ----
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.45in, top=0.4in, bottom=0.4in]{geometry}
\usepackage{tgheros}                % Helvetica-like sans-serif
\renewcommand{\familydefault}{\sfdefault}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{tabularx}

% ---- No page numbers ----
\pagestyle{empty}

% ---- Colors ----
\definecolor{accent}{HTML}{1a2332}
\definecolor{link}{HTML}{2563eb}
\definecolor{divider}{HTML}{94a3b8}
\definecolor{light}{HTML}{64748b}

% ---- Hyperlinks ----
\hypersetup{
  colorlinks=true,
  linkcolor=link,
  urlcolor=link,
  pdfauthor={S. Parker Singleton},
  pdftitle={Resume},
}

% ---- Section Formatting ----
\titleformat{\section}
  {\normalsize\bfseries\color{accent}}
  {}
  {0em}
  {\MakeUppercase}
  [\vspace{-0.7em}{\color{divider}\rule{\linewidth}{0.5pt}}]

\titlespacing*{\section}{0pt}{0.6em}{0.25em}

% ---- List Formatting ----
\setlist[itemize]{leftmargin=1.2em, itemsep=0pt, parsep=0pt, topsep=1pt, label={\textcolor{divider}{\textbullet}}}

% ---- Paragraph spacing ----
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---- Custom Commands ----
\newcommand{\roleentry}[4]{%
  \textbf{#1} \hfill \textcolor{light}{\small #2} \\[-0.15em]
  {\small\textit{#3} \hfill #4}
  \vspace{0.15em}
}

\newcommand{\me}{\textbf{S.\ P.\ Singleton}}

% ============================================================
\begin{document}

% ---- Header ----
\begin{center}
  {\LARGE\bfseries\color{accent} S.\ Parker Singleton}\\[0.25em]
  {\small
    \href{mailto:sps253@cornell.edu}{sps253@cornell.edu}
    \enspace$\vert$\enspace
    \href{https://singlesp.github.io}{singlesp.github.io}
    \enspace$\vert$\enspace
    \href{https://sypres.io}{sypres.io}
  }
\end{center}

\vspace{0.15em}

% ================================================================
\section{Experience}
% ================================================================

\roleentry{Senior Scientist}{Aug 2025 -- Present}
  {Penn Lifespan Informatics \& Neuroimaging Center, University of Pennsylvania}{Philadelphia, PA}
\begin{itemize}
  \item Lead researcher and developer for \href{https://sypres.io}{SYPRES}: living evidence synthesis platform for clinical psychedelic research.
  \item Member of the neuroinformatics team: neuroimaging data curation, analysis, release; full-stack software engineering.
\end{itemize}
\vspace{0.2em}

\roleentry{Postdoctoral Researcher}{May 2024 -- Jul 2025}
  {Penn Lifespan Informatics \& Neuroimaging Center, University of Pennsylvania}{Philadelphia, PA}
\begin{itemize}
  \item Assessed clinical efficacy and risks of psychedelic-assisted therapies using fMRI and computational modeling.
  \item Developed novel frameworks for quantifying psychedelic-induced functional brain plasticity.
\end{itemize}
\vspace{0.2em}

\roleentry{Postdoctoral Researcher}{Apr 2023 -- Apr 2024}
  {Computational Connectomics Lab, Weill Cornell Medicine}{New York, NY}
\begin{itemize}
  \item Applied network control theory and multimodal neuroimaging to study pharmacological effects on brain dynamics.
  \item Mentored undergraduate and graduate students on rotation and thesis projects.
\end{itemize}
\vspace{0.2em}

\roleentry{NSF Graduate Research Fellow}{Jun 2020 -- Apr 2023}
  {Department of Computational Biology, Cornell University}{Ithaca, NY}
\begin{itemize}
  \item Identified neural correlates of MDMA-assisted therapy for PTSD via audio script-driven fMRI paradigms.
  \item Published first-author papers in \textit{Nature Communications} and \textit{Frontiers in Psychiatry}.
\end{itemize}
\vspace{0.2em}

\roleentry{High School Teacher}{Aug 2017 -- Jun 2020}
  {Palmetto Scholars Academy}{North Charleston, SC}
\begin{itemize}
  \item Designed chemistry curricula for gifted students; taught dual-enrollment college chemistry and research methods.
\end{itemize}

% ================================================================
\section{Education}
% ================================================================

\textbf{Ph.D.\ Computational Biology} \hfill Cornell University, 2023 \\
\textbf{M.S.\ Chemistry} \hfill Cornell University, 2017 \\
\textbf{B.S.\ Chemistry} \hfill University of South Carolina, 2015

% ================================================================
\section{Selected Publications}
% ================================================================

{\small
\begin{enumerate}[leftmargin=1.5em, itemsep=2pt, parsep=0pt, topsep=2pt]
  \item Mallaroni, \me, et al.\ ``Spatiotemporal mapping of brain organisation following 2C-B and psilocybin.'' \textit{Mol.\ Psychiatry}, 2026.

  \item \me, et al.\ ``An initiative for living evidence synthesis in clinical psychedelic research.'' \textit{Nat.\ Ment.\ Health}, 2025.

  \item \me, Timmermann, et al.\ ``Network control energy reductions under DMT relate to serotonin receptors, signal diversity, and subjective experience.'' \textit{Commun.\ Biol.}, 2025.

  \item \me, Luppi, et al.\ ``Receptor-informed network control theory links LSD and psilocybin to a flattening of the brain's control energy landscape.'' \textit{Nat.\ Commun.}, 2022.

  \item \me, Wang, et al.\ ``Altered brain activity and functional connectivity after MDMA-assisted therapy for PTSD.'' \textit{Front.\ Psychiatry}, 2023.
\end{enumerate}
\vspace{0.1em}
\textcolor{light}{\textit{Full list: 13 original research articles \& 2 commentaries across Nature Communications, Nature Biomedical Engineering, Nature Human Behaviour, Nature Mental Health, Molecular Psychiatry, Communications Biology, and others.}}
}

% ================================================================
\section{Skills \& Expertise}
% ================================================================

{\small
\begin{tabularx}{\linewidth}{@{}lX@{}}
  \textbf{Neuroimaging} & fMRI, dMRI, ASL preprocessing and analysis; network neuroscience; biomarker discovery \\
  \textbf{Computation} & Meta-analysis, machine learning, statistics, dynamical systems modeling \\
  \textbf{Programming} & Python, R, MATLAB, Bash, Git, full-stack web development \\
  \textbf{Domain} & Psychedelic neuroscience, substance use disorders, PTSD, clinical trial methodology \\
\end{tabularx}
}

% ================================================================
\section{Selected Honors}
% ================================================================

{\small
\begin{tabularx}{\linewidth}{@{}lX@{}}
  2022 & Fulbright Research Grant Alternate \\
  2016--2022 & National Science Foundation Graduate Research Fellowship \\
  2014 & Hiram S.\ and Lawanda Allen Scholarship for Excellence in Chemistry \\
  2014 & Magellan Scholarship for Undergraduate Research \\
\end{tabularx}
}

% ================================================================
\section{Selected Presentations}
% ================================================================

{\small
\begin{itemize}
  \item \textbf{Invited:} Winter Conference on Brain Research (2025); NIAAA / Nora Volkow Group (2023); OPEN Foundation (2023); Maastricht University (2022); Oxford Psychedelic Society (2021).
  \item \textbf{Posters:} ACNP (2026); Gordon Research Conference (2025); OHBM (2021--2024); Psychedelic Science (2023).
\end{itemize}
}

\end{document}

